\Large \bf Lissy: Experimenting with on-chain order books

### 2022-06-01 LaTeX-LNCS-2022/main.tex
some notes/comments added
cutting the text down to 23 pages
reorg / new sections added (down to 21 pages)
top matter [19 pages total]
morre changes
hooks for improvements
wtsc changes

\title{\Large \bf Trading On-chain: How Feasible Is Regulators' Worst-Case Scenario?}

\author{Mahsa Moosavi\inst{1} \and Jeremy Clark\inst{1}}
\institute{Concordia University, Montreal, Canada}

@@

@@

\clearpage
\bibliography{bib/DEX}
%\nocite{*}

@@

\clearpage
\appendix
\input{sections/appendix.tex}

>>>>

\title{\Large \bf Lissy: Experimenting with on-chain order books}

\author{Mahsa Moosavi \and Jeremy Clark}
\institute{Concordia University, Montreal, Canada \\ \email{seye\_moo@encs.concordia.ca}}

@@

% = = = = = Acknowledgements = = = = = %

\subsubsection*{Acknowledgements.}  The authors thank the AMF (Autorité des Marchés Financiers) for supporting this research project. J. Clark also acknowledges partial funding from the National Sciences and Engineering Research Council (NSERC)/Raymond Chabot Grant Thornton/Catallaxy Industrial Research Chair in Blockchain Technologies, as well as NSERC through a Discovery Grant. M. Moosavi acknowledges support from Fonds de Recherche du Québec - Nature et Technologies (FRQNT).

@@

\bibliography{bib/DEX}
%\nocite{*}

@@

\appendix
\input{sections/appendix.tex}
